---
title: "HW wk 2"
author: "Suzanna Storms"
date: "9/8/2020"
output: html_document
---
---
title: "Week 2 HW"
author: "Suzanna Storms"
date: "9/7/2020"
output: html_document
---
Create an R Markdown document and do the following (include the R code in all of your answers):

     a) show the step-by-step how to solve the following system of equations in R (Use R chunks to run each part). 

      2x + 5y = 33
      x + 3y = 19
      
```{r}
C <-matrix(data=c(2, 5, 1, 3), nrow=2, ncol=2, byrow = TRUE)
d<-matrix(data=c(33, 19), nrow=2, ncol=1, byrow=FALSE)
round(solve(C, d), 2)


```

b) create a vector that goes from 1 to 100 and calculates the average of it WITHOUT using the R function “mean”.

```{r}
v <- 1:100; v
median(v)
```


c) install the package “dplyr”.
nstall.packages("dplyr")
trying URL 'https://cran.rstudio.com/bin/macosx/el-capitan/contrib/3.6/dplyr_1.0.2.tgz'
Content type 'application/x-gzip' length 1217346 bytes (1.2 MB)
==================================================
downloaded 1.2 MB


The downloaded binary packages are in
	/var/folders/yz/_8f8dt4n5w59n9w7w8ygprgh0000gn/T//RtmpQzUCK5/downloaded_packages
```
3 - create a data frame of two rows with A, B, C, and D in row 1 and D, E, F, and G in row 2.
```{r}
row_1 <- c("A, B, C, D")
row_2 <- c("D, E, F, G")
DF <- data.frame(row_1, row_2, stringsAsFactors = FALSE)
str(DF)

#4 - Create a repository on your GitHub account (not in the IntroToR organization!) and push the R Markdown file created on #2.


